Constructing composite ordinal outcomes for clinical trials

### 2025-09-15 constructing_ordinal_outcomes.tex
Tweaking

@@

One point of view is that one would ``ideally'' analyze ordinal outcomes by
reporting the associated expected utilities \todo{cite Berry talk; example of
utility-weighted Rankin scale} and that since existing ordinal methods supply
such utilities implicitly why not just supply them explicitly. A counterpoint
is that the methods do not, in fact, supply utilities implicitly. Another is
that ordinal outcomes let one ``hedge'' about precise utilities and this is
OK: fully-specified utility function may require more extensive development and
validation or may vary widely across patients.

>>>>

This should also hold \emph{within strata}.

@@

One point of view is that one would ``ideally'' analyze ordinal outcomes by
reporting the associated expected utilities \todo{cite Berry talk; possibly
cite Lumley blog post; example of utility-weighted Rankin scale} and that since
existing ordinal methods supply such utilities implicitly why not just supply
them explicitly. A counterpoint is that the methods do not, in fact, supply
utilities implicitly. Another is that ordinal outcomes let one ``hedge'' about
precise utilities and this is OK: fully-specified utility function may require
more extensive development and validation or may vary widely across patients.
